Regression Discontinuity Design to Measure Incumbency Advantage in US Congressional Elections

### 2023-04-20 sandbox/STAT530_ProjectSlides.qmd
Add files via upload

  * Introduction to Regression Discontinuity Design
  * RRD Applied to US Congressional Elections: The Setup
  * [ADD LATER]
  * [ADD LATER]

@@

  * **Introduction to Regression Discontinuity Design**
  * RRD Applied to US Congressional Elections: The Setup
  * [ADD LATER]
  * [ADD LATER]

@@

  * Introduction to Regression Discontinuity Design
  * **RRD Applied to US Congressional Elections: The Setup**
  * [ADD LATER]
  * [ADD LATER]

@@

  * U.S. House 1976–2020 Elections
      * MIT Election Data and Science Lab, 2017, "U.S. House 1976–2020"
  * Historical Congressional Legislation and District Demographics 1972-2014
      * Foster-Molina, Ella, 2017, "Historical Congressional Legislation and District Demographics 1972-2014"

@@

>>>>

  * Introduction to Regression Discontinuity Design
  * RDD Applied to US Congressional Elections: The Setup
  * RDD Applied to US Congressional Elections: Results
  * RDD Applied to US Congressional Elections: Conclusions

@@

  * Introduction to Regression Discontinuity Design
  * RDD Applied to US Congressional Elections: The Setup
  * RDD Applied to US Congressional Elections: Results
  * RDD Applied to US Congressional Elections: Conclusions

@@

  * Introduction to Regression Discontinuity Design
  * **RDD Applied to US Congressional Elections: The Setup**
  * RDD Applied to US Congressional Elections: Results
  * RDD Applied to US Congressional Elections: Conclusions

@@

@@

  * Introduction to Regression Discontinuity Design
  * RDD Applied to US Congressional Elections: The Setup
  * **RDD Applied to US Congressional Elections: Results**
  * RDD Applied to US Congressional Elections: Conclusions
